---
title: Shiny on your github.io
author: Simon Steiger
date: '2017-09-27'
slug: shiny-on-your-github-io
categories:
  - R
  - Shiny
tags:
  - Shiny
  - plot
runtime: shiny
---

# How to blog with an embedded shiny application

The challenge to have a embedded shiny-applications is, that it needs to run on a public R-Server. 

Link to [Tutorial](https://shiny.rstudio.com/tutorial/written-tutorial/lesson1/) I'm following. 


This allows you to create a Shinyapp and include it in a blogpost or rendered html Output of any sort.
Here I will show how to create an simple example App, how to deploy it to shinyapps.io and how to include it in the html output of your Rmarkdown file.


# Code to create a shiny app:
Two files are needed to create a shiny app. `ui.R` and `server.R`

The app will be created in the folder where your Rmarkdown is rendered. 
The name of the folder could be the name of the App you want to create:

```{r appname}
appName <- "Shinyapp_1"
```

## UI to create an interactive histogram:  

saved as `Shinyapp_1/ui.R`

```{r ui, code=readLines("Shinyapp_1/ui.R"),eval=FALSE,background="#006EB8"}
```

## R script that works as the server logic:
saved as `Shinyapp_1/server.R`

```{r server, code=readLines("Shinyapp_1/server.R"),eval=FALSE,background="#006EB8"}
```

Simple call to open shiny webapp inside R terminal
This does not work if you want to post an html independent of your local R-Session. To include a shiny app in your blog-post you need to publish the app to a r-server, as for example shinyapps.io. This is due to your github.io blog beign a static website without any server-side R running.


```{r eval=FALSE}
shiny::shinyAppDir("Shinyapp_1/")
```

To deploy an app to shinyapps.io you need the package rsconnect and an account.  
Here I will go through the steps to create a shiny app on shinyapps.io and link to it inside of you rmarkdown file.  
Steps to set up your shinyapps.io account with rsconnect: 
[shinapps.io](http://docs.rstudio.com/shinyapps.io/getting-started.html)
First you need to connect your local r session to shinyapps.io:

```{r, eval=FALSE}
rsconnect::setAccountInfo(name='simontuk', token='<TOKEN>', secret='<SECRET>')
```


```{r warning=FALSE,echo=FALSE}
appExists <- tolower(appName) %in% rsconnect::applications()$name
```

Then you can deploy the app with rsconnect: 

```{r eval=!appExists}
rsconnect::deployApp("Shinyapp_1/",appName = tolower(appName),launch.browser = FALSE)
```

The apps are hosted on shinyapps.io in the format:
https://<<your_username>>.shinyapps.io/<<appName>>/
With the help of the `knitr::include_app()` Function you can embedd the app we just created into the html that will be posted as a static file on your blog. The app will still run on shinyapps.io, but the user can interact with the app without leaving your blog post.

```{r}
AppUrl <- paste0("https://simontuk.shinyapps.io/",tolower(appName),"/")

knitr::include_app(url = AppUrl,
  height = "600px")
```


