---
title: Shiny on your github.io
author: Simon Steiger
date: '2017-09-27'
slug: shiny-on-your-github-io
categories:
  - R
  - Shiny
tags:
  - Shiny
  - plot
runtime: shiny
---

# How to write a .rmd so you will host a shiny application on your homepage in the end?


Create the UI for the app. Link to [Tutorial](https://shiny.rstudio.com/tutorial/written-tutorial/lesson1/) I'm following.

## UI to create an interactive histogram:  

saved as `Shinyapp_1/ui.R`
```{r ui, code=readLines("Shinyapp_1/ui.R"),eval=FALSE,background="#006EB8"}
```

## R script that works as the server logic:
saved as `Shinyapp_1/server.R`
```{r server, code=readLines("Shinyapp_1/server.R"),eval=FALSE,background="#006EB8"}
```

Simple call to open shiny webapp inside R terminal
This does not work on your blogdown blog as it is a static website without any server-side R running.


```{r warning=FALSE}
appName <- "Shinyapp_1"
appExists <- tolower(appName) %in% rsconnect::applications()$name
```

```{r eval=!appExists}
a <- rsconnect::deployApp("Shinyapp_1/",appName = tolower(appName),launch.browser = FALSE)
```

```{r}
AppUrl <- paste0("https://simontuk.shinyapps.io/",tolower(appName),"/")

```

## So how to link to a runnign shiny app for interactive visualization?
Here I will go through the steps to create a shiny app on shinyapps.io and link to it inside of you rmarkdown file.  


Steps to set up your shinyapps.io account with rsconnect: 
[shinapps.io](http://docs.rstudio.com/shinyapps.io/getting-started.html)

```{r}
knitr::include_app(AppUrl, 
  height = "600px")
```


